\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2019-06-05 sections/methods.tex
Add: Add item
Add: Line about db consensus algorithm and magma ref

  \subsection*{Taxonomy Assignment}
  \vspace{-5mm}
  This module deals with assigning taxonomies to either the representative sequences of the \ac{otu}s or directly to the \ac{esv}s.
  In order to assign taxonomies to a particular sequence we use:
  \begin{itemize}
    \item A taxonomy database, which is a collection of 16S sequences of known organisms.
    \item A query tool, which allows one to compare a sequence of interest to all the sequences in the database to find the best match.
  \end{itemize}
  The pipeline incorporates \ac{gg}~\cite{DeSantis2006}, SILVA~\cite{Quast2012} and the \ac{ncbi}~\cite{Sayers2009} databases for taxonomy assignment and the Naive Bayes classifier from \ac{qiime2} and \ac{ncbi} blast as the query tools.

@@

  \subsection*{Network Inference}
  \vspace{-5mm}
  This module deals with the inference of co-occurrence associations from the \ac{otu} or \ac{otu} counts matrix.
  These associations can be represented as a network, with nodes representing taxonomies and edges the association between them.
  \begin{itemize}
    \item A null model is created by re-sampling and bootstrapping the correlation/interaction matrix
    \item Significance of these associations is determined by calculating pvalues against this null model.
  \end{itemize}
  The pipeline includes Pearson, Spearman and \ac{sparcc}~\cite{Friedman2012} as the pairwise correlation metrics, and \ac{spieceasi}~\cite{Kurtz2015}, \ac{mldm}~\cite{Yang2017} and \ac{magma}~\cite{} as the direct association metrics.

>>>>

  \subsection*{Taxonomy Assignment}
  \vspace{-5mm}
  This module deals with assigning taxonomies to either the representative sequences of the \ac{otu}s or directly to the \ac{esv}s.
  In order to assign taxonomies to a particular sequence we use:
  \begin{itemize}
    \item A taxonomy database, which is a collection of 16S sequences of known organisms.
    \item A query tool, which allows one to compare a sequence of interest to all the sequences in the database to find the best match.
    \item Consensus method
  \end{itemize}
  The pipeline incorporates \ac{gg}~\cite{DeSantis2006}, SILVA~\cite{Quast2012} and the \ac{ncbi}~\cite{Sayers2009} databases for taxonomy assignment and the Naive Bayes classifier from \ac{qiime2} and \ac{ncbi} blast as the query tools (from \ac{qiime2}).
  The consensus algorithm used is also defaults used by the classifiers in \ac{qiime2}.

@@

  \subsection*{Network Inference}
  \vspace{-5mm}
  This module deals with the inference of co-occurrence associations from the \ac{otu} or \ac{otu} counts matrix.
  These associations can be represented as a network, with nodes representing taxonomies and edges the association between them.
  \begin{itemize}
    \item A null model is created by re-sampling and bootstrapping the correlation/interaction matrix
    \item Significance of these associations is determined by calculating pvalues against this null model.
  \end{itemize}
  The pipeline includes Pearson, Spearman and \ac{sparcc}~\cite{Friedman2012} as the pairwise correlation metrics, and \ac{spieceasi}~\cite{Kurtz2015}, \ac{mldm}~\cite{Yang2017} and \ac{magma} (\hl{in biorxiv}) as the direct association metrics.
